### 2015-07-20 src/misc/s6_thanks.tex
Updated word of thanks.

Many people have contributed to my social and professional development over the course of my PhD. I would therefore like to extend my thanks to my friends, colleagues, and family for a wonderful six years.

\textbf{Pieter}, you are an amazing researcher and I'm proud to have been your student. I admire your sense of pragmatism and focus. And, I must admit that, even though our (sometimes heated) discussions, you have greatly influenced my writing style for the better. \textbf{Luc}, you greatly helped me iron out the detail in my experimental procedures, and provided crucial feedback when I was stuck analyzing our data. After receiving yet another batch of comments on one of my manuscripts, you were always there to provide support and to help me formulate a proper response. Many thanks to both of you!

>>>>

Many people have contributed to my social and professional development over the course of my PhD. I would therefore like to extend my thanks to my friends, colleagues, and family for these wonderful six years.

\textbf{Pieter}, you are an amazing researcher and I'm proud to have been your student. I admire your sense of pragmatism and focus. Even though our (sometimes heated) discussions, I must admit that you have greatly influenced my writing style for the better. \textbf{Luc}, you greatly helped me iron out the detail in my experimental procedures, and provided crucial feedback when I was stuck analyzing our data. After receiving yet another batch of comments on one of my manuscripts, you were always there to provide support and to help me formulate a proper response. Many thanks to both of you!
